A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-18 documents/plm.tex
metadata

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{PLM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\todo}[1]{\textbf{#1}}

@@

The model is
We specify what likelihood and what regularization?
\todo{foo:}
\begin{eqnarray}
I_{mn}         &=& I^{\ast}_{mn} + \mbox{noise}
\\
I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n}
\quad,
\end{eqnarray}
where \todo{bar}
\begin{eqnarray}
\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mn'}]^2}{\sigma^2_{mn'}}
                 + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
\\
I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
\quad,
\end{eqnarray}
where \todo{bar}

>>>>

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{PLM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\given}{\,|\,}
\newcommand{\todo}[1]{\textbf{#1}}

@@

In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
  used to make each prediction, we will use also some \emph{meta-data};
  these include the time itself $t_n$,
  the sine and cosine of the parallactic angle $\theta(t_n)$,
  and the dot product $\hat{n}\cdot v(t_n)$ of the spacecraft velocity $v(t_n)$
  with the direction $\hat{n}$ towards the \Kepler\ field center.
These additional meta-data variables permit the data-driven model
  to capture easily variations induced in the data
  by proper motions, parallaxes, and stellar aberration.
Symbolically, we will denote these $K=4$ pieces of meta-data $d_{kn}$.

As mentioned above, in the context of this project,
  a model is something that can predict data given settings of some parameters,
  and an objective function that can be used to find best values for those parameters.
We prefer to work in a probabilistic mode in which the objective function can be justified
  in terms of a likelihood (probability for the data given the model)
  or a posterior probability density function (likelihood times a prior pdf).
The PLM treats the noise in a \Kepler\ pixel $m$ at time $n$ as Gaussian (normally distributed)
  with mean zero and known variance $\sigma^2_{mn}$,
  and the expectation value for each \Kepler\ data point $I_{mn}$ as being
  predictable from a linear combination of data points $I_{m'n}$,
  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
This linear model has parameters (linear coefficients) $a_{mm'}$.
\todo{foo:}
\begin{eqnarray}
I_{mn}         &=& I^{\ast}_{mn} + e_{mn}
\\
I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mk}\,d_{kn}
\\
p(e_{mn})      &=& N(e_{mn}\given 0,\sigma^2_{mn})
\quad,
\end{eqnarray}
where HOGGGGGGGGGGGGGGGGGGGGGGGG
\begin{eqnarray}
\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mn'}]^2}{\sigma^2_{mn'}}
                 + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
\\
I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
\quad,
\end{eqnarray}
where \todo{bar}
